---
title: "MARK 1 (beta)"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    logo: GDOTLogo.svg
    favicon: GDOTLogo.svg 
    css: style.css
    includes:
        in_header: google-analytics.html
runtime: shiny
---


```{r global, cache = TRUE, include = FALSE, warning = FALSE}
# FLEXDASHBOARD - RTOP_MONTHLY_REPORT_-_BETA


source("Monthly_Report_UI_Functions.R")


FIG_WIDTH = 14
FIG_HEIGHT = 7

```









Inputs {.sidebar}
=====================================

Measurement, Accuracy, and Reliability Kit (MARK 1) 

Past month reports can be viewed back to `r tail(conf$report_months, 1)`.

```{r sidebar, warning = FALSE, cache = FALSE}
# shiny inputs defined here

month_options <- conf$report_months

zone_group_options <- conf$zone_groups

selectInput("month", "Month:",
                       choices = month_options,
                       selected = conf$selected_month)

selectInput("zone_group", "Signal Group:",
                       choices = zone_group_options,
                       selected = "All RTOP")



# DRILL DOWN WITHIN CORRIDORS TO SEE ALL SIGNALS
conditionalPanel("input.zone_group == 'RTOP1'",
                 selectInput("corridor_rtop1", "Corridor",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "RTOP1")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'RTOP2'",
                 selectInput("corridor_rtop2", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "RTOP2")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'D1'",
                 selectInput("corridor_d1", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "D1")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'D3'",
                 selectInput("corridor_d3", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "D3")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'D4'",
                 selectInput("corridor_d4", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "D4")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'D5'",
                 selectInput("corridor_d5", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "D5")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'D6'",
                 selectInput("corridor_d6", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "D6")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'Zone 7'",
                 selectInput("corridor_z7", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "Zone 7")$Corridor
                                         ))),
                             selected = "All Corridors"))

conditionalPanel("input.zone_group == 'Cobb County'",
                 selectInput("corridor_cb", "Corridor:",
                             choices = c("All Corridors", 
                                         as.character(unique(filter(
                                             corridors, Zone_Group == "Cobb County")$Corridor
                                         ))),
                             selected = "All Corridors"))

current_month <- reactive(lubridate::dmy(paste(1, input$month)))
current_quarter <- reactive(as.character(lubridate::quarter(current_month(), with_year = TRUE)))


corridor <- reactive(
    if (input$zone_group == "RTOP1") {
        input$corridor_rtop1
    } else if (input$zone_group == "RTOP2") {
        input$corridor_rtop2
    } else if (input$zone_group == "D1") {
        input$corridor_d1
    } else if (input$zone_group == "D3") {
        input$corridor_d3
    } else if (input$zone_group == "D4") {
        input$corridor_d4
    } else if (input$zone_group == "D5") {
        input$corridor_d5
    } else if (input$zone_group == "D6") {
        input$corridor_d6
    } else if (input$zone_group == "Zone 7") {
        input$corridor_z7
    } else if (input$zone_group == "Cobb County") {
        input$corridor_cb
    } else {
        "All Corridors"
    })

    
zone_group <- reactive(
    if (corridor() == "All Corridors") {
        input$zone_group
    } else {
        corridor()
    }
)


mr <- reactive(
    if (corridor() == "All Corridors") {
        cor
    } else {
        sig
    }
)


filtered_corridors <- reactive({
    if (input$zone_group == "All RTOP") {
        zg_ <- c("RTOP1", "RTOP2")
    } else {
        zg_ <- input$zone_group
    }

    if (corridor() == "All Corridors") {
        corridors %>%
            filter(Zone_Group %in% zg_) %>%
            select(-Description, -Asof)
    } else {
        corridors %>%
            filter(Corridor == corridor()) %>%
            select(-Description, -Asof)
    }
})

filtered_signalids <- reactive(paste0(filtered_corridors()$SignalID, ": ",
                                      filtered_corridors()$Name))

# renderText({"\nSelected Month"})
# renderPrint({current_month()})

# renderText({"Selected Zone Group"})
# renderPrint({zone_group()})

# renderText({"Selected Corridor"})
# renderPrint({corridor()})
```









One-Month Summary
=====================================

Row {data-height = 50}
-------------------------------------

### Performance <a id = "page_performance"></a>

Arterial performance measures (% change from previous month)

Row
-------------------------------------

### Throughput [vph] {.value-box}

```{r cache = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$tp, "vph", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-bar-chart",
    color = BLUE
  )
})
```

### Arrivals on Green {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$aogd, "aog", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-car",
    color = BLUE
  )
})
```

### Spillback Rate {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$qsd, "qs_freq", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-car",
    color = BLUE
  )
})
```

### Split Failures {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$sfd, "sf_freq", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-car",
    color = BLUE
  )
})
```

### Travel Time Index {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$tti, "tti", as_2dec, 
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-dashboard",
    color = BLUE
  )
})
```

### Planning Time Index {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$pti, "pti", as_2dec, 
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-dashboard",
    color = BLUE
  )
})
```


Row {data-height = 50}
-------------------------------------

### Volume-Based Measures

Corridor volumes (% change from previous month)

Row
-------------------------------------


### Traffic Volume [veh/day] {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(mr()$mo$vpd, "vpd", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart",
    color = BLUE
  )
})
```

### AM Peak Volume [veh/hr] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$vphp$am, "vph", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-area-chart",
    color = BLUE
  )
})
```

### PM Peak Volume [veh/hr] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$vphp$pm, "vph", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-area-chart",
    color = BLUE
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = NULL,
    icon = NULL,
    color = "gray80"
  )
})
```

Row {data-height = 50}
-------------------------------------

### Equipment Measures

Device and Communications Uptime (% change from previous month)

Row
-------------------------------------

### Vehicle Detector Availability [manually collected] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$veh, "uptime", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-car",
    color = BLUE
  )
})
```

### Pedestrian Detector Availability [manually collected] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$ped, "uptime", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-child",
    color = BLUE
  )
})
```

### CCTV Availability {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(mr()$mo$cctv, "uptime", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "glyphicon-facetime-video",
    color = BLUE
  )
})
```

### Communications Uptime {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$cu, "uptime", as_pct, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "ion-paper-airplane", #"fa-user" #
    color = BLUE
  )
})
```


Row {data-height = 50}
-------------------------------------

### Activity Measures

Activity measures from TEAMS and as reported by Traffic Engineers (% change from previous month)

Row
-------------------------------------

### TEAMS Tasks Reported This Month {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(rename(cor$mo$events, delta = delta.rep), "Reported", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart",
    color = BLUE
  )
})
```

### TEAMS Tasks Resolved This Month {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(rename(cor$mo$events, delta = delta.res), "Resolved", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart",
    color = BLUE
  )
})
```

### TEAMS Tasks Outstanding [Unresolved] {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(rename(cor$mo$events, delta = delta.out), "Outstanding", as_int, 
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart",
    color = BLUE
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = NULL,
    icon = NULL,
    color = "gray80"
  )
})
```









Quarter Summary
=====================================

Row {data-height = 50}
-------------------------------------

### Performance

Arterial performance measures (% change from previous quarter)

Row
-------------------------------------

### Throughput [vph] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$tp, "vph", as_int, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = TRUE),
      icon = "fa-bar-chart",
      color = GDOT_BLUE
  )
})
```

### Arrivals on Green {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$aogd, "aog", as_pct, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = TRUE),
      icon = "fa-car",
      color = GDOT_BLUE_RGB
  )
})
```

### Spillback Rate {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$qsd, "qs_freq", as_pct, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = TRUE),
      icon = "fa-car",
      color = GDOT_BLUE
  )
})
```

### Split Failures {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$sfd, "sf_freq", as_pct, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = TRUE),
      icon = "fa-car",
      color = GDOT_BLUE_RGB
  )
})
```

### Travel Time Index {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$tti, "tti", as_2dec, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = TRUE),
      icon = "fa-dashboard",
      color = GDOT_BLUE
  )
})
```

### Planning Time Index {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$pti, "pti", as_2dec, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = TRUE),
      icon = "fa-dashboard",
      color = GDOT_BLUE_RGB
  )
})
```


Row {data-height = 50}
-------------------------------------

### Volume-Based Measures

Corridor volumes (% change from previous quarter)

Row
-------------------------------------


### Traffic Volume [veh/day] {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(cor$qu$vpd, "vpd", as_int, 
                           zone = zone_group(), 
                           mo = current_month(), 
                           qu = current_quarter(), break_ = FALSE),
    icon = "fa-area-chart",
      color = GDOT_YELLOW_RGB
  )
})
```

### AM Peak Volume [veh/hr] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$vphpa, "vph", as_int, 
                           zone = zone_group(), 
                           mo = current_month(),
                           qu = current_quarter(), break_ = FALSE),
      icon = "fa-area-chart",
      color = GDOT_YELLOW
  )
})
```

### PM Peak Volume [veh/hr] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$vphpp, "vph", as_int, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
      icon = "fa-area-chart",
      color = GDOT_YELLOW_RGB
  )
})
```


### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = NULL,
    icon = NULL,
    color = "gray80"
  )
})
```

Row {data-height = 50}
-------------------------------------

### Equipment Measures

Device and Communications Uptime (% change from previous quarter)

Row
-------------------------------------

### Vehicle Detector Availability [manually collected] {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$veh, "uptime", as_pct, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
      icon = "fa-car",
      color = GDOT_BLUE
  )
})
```

### Pedestrian Detector Availability [manually collected] {.value-box}

```{r}

renderValueBox({
  valueBox(
    value = get_valuebox(cor$qu$ped, "uptime", as_pct, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
    icon = "fa-child",
      color = GDOT_BLUE_RGB 
  )
})
```

### CCTV Availability {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(cor$qu$cctv, "uptime", as_pct, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
    icon = "glyphicon-facetime-video",
      color = GDOT_BLUE 
  )
})
```

### Communications Uptime {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$cu, "uptime", as_pct, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
      icon = "ion-paper-airplane",
      color = GDOT_BLUE_RGB
  )
})
```


Row {data-height = 50}
-------------------------------------

### Activity Measures

Activity measures from TEAMS and as reported by Traffic Engineers (% change from previous quarter)

Row
-------------------------------------

### TEAMS Tasks Reported This Quarter {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$qu$reported, "Reported", as_int, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
      icon = "fa-area-chart",
      color = GDOT_YELLOW
  )
})
```

### TEAMS Tasks Resolved This Quarter {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(cor$qu$resolved, "Resolved", as_int, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
    icon = "fa-area-chart",
      color = GDOT_YELLOW_RGB
  )
})
```

### TEAMS Tasks Outstanding [Unresolved] {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = get_valuebox(cor$qu$outstanding, "Outstanding", as_int, 
                         zone = zone_group(), 
                         mo = current_month(), 
                         qu = current_quarter(), break_ = FALSE),
    icon = "fa-area-chart",
      color = GDOT_YELLOW
  )
})
```

### {.value-box}

```{r}
renderValueBox({
  valueBox(
    value = NULL,
    icon = NULL,
    color = "gray80"
  )
})
```









Summary Trend
=====================================

Row
-------------------------------------

### Performance


```{r summary_left, eval = TRUE, warning = FALSE}
fillCol(
    renderPlotly({ 
        data.set <- filter(mr()$mo$tp, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "vph", "Throughput", RED2, as_int) 
    }),
    renderPlotly({ 
        data.set <- filter(mr()$mo$aogd, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "aog", "Arrivals on Green\nGoal: 80%", RED2, as_pct, ".1%") 
    }),
    renderPlotly({ 
        data.set <- filter(mr()$mo$qsd, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "qs_freq", "Queue\nSpillback", RED2, as_pct, ".1%")
    }),
    renderPlotly({ 
        data.set <- filter(mr()$mo$sfd, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "sf_freq", "Split\nFailure", RED2, as_pct, ".1%")
    }),
    renderPlotly({ 
        data.set <- filter(cor$mo$tti, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "tti", "Travel Time\nIndex", RED2, as_2dec, ".2f") 
    }),
    renderPlotly({ 
        data.set <- filter(cor$mo$pti, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "pti", "Planning Time\nIndex", RED2, as_2dec, ".2f")
    }),
    height = 700)
```

### Volumes and Equipment

```{r summary_right, eval = TRUE, warning = FALSE}

fillCol(
    renderPlotly({ 
        data.set <- filter(mr()$mo$vpd, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "vpd", "Daily\nVolume", GDOT_BLUE, as_int)
    }),
    
    renderPlotly({ 
        data.set <- filter(mr()$mo$vphp$am, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "vph", "AM Hourly\nVolume", GDOT_BLUE, as_int)
    }),
    renderPlotly({ 
        data.set <- filter(mr()$mo$vphp$pm, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "vph", "PM Hourly\nVolume", GDOT_BLUE, as_int)
    }),

    renderPlotly({ 
        data.set <- filter(cor$mo$du, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "uptime.all", "Detector\nUptime\nGoal: 95%", ORANGE, as_pct, ".1%")
    }),
    renderPlotly({ 
        data.set <- filter(cor$mo$ped, 
                          Corridor==zone_group() & Month <= current_month() & Month >= ymd("2017-07-01"))
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "uptime", "Ped Detector\nUptime\nGoal: 95%", ORANGE, as_pct, ".1%")
    }),
    renderPlotly({ 
        data.set <- filter(mr()$mo$cctv, 
                          Corridor==zone_group() & Month <= current_month() & Month >= ymd("2017-07-01"))
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "uptime", "CCTV\nUptime\nGoal: 95%", ORANGE, as_pct, ".1%")
    }),
    renderPlotly({ 
        data.set <- filter(mr()$mo$cu, Corridor==zone_group() & Month <= current_month())
        validate(need(nrow(data.set) > 0, "No Data"))
        perf_plot(data.set, "uptime", "Communications\nUptime\nGoal: 95%", ORANGE, as_pct, ".1%")
    }),
    height = 800)
```









Performance
=====================================

Row
-------------------------------------

### Throughput (vph) {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$tp, "vph", as_int,
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-bar-chart"
  )
})
```

### Arrivals on Green {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$aogd, "aog", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-car"
  )
})
```

### Spillback Rate {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$qsd, "qs_freq", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-car"
  )
})
```

### Split Failures {.value-box}

```{r}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$sfd, "sf_freq", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-car"
  )
})
```

### Travel Time Index {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$tti, "tti", as_2dec,
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-dashboard"
  )
})
```

### Planning Time Index {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$pti, "pti", as_2dec,
                           zone = zone_group(), mo = current_month(), break_ = TRUE),
      icon = "fa-dashboard"
  )
})
```


Row {.tabset .tabset-fade}
-------------------------------------


### Throughput

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({
    get_bar_line_dashboard_plot(mr()$wk$tp, mr()$mo$tp, NULL,
                                "vph", "integer", highlight_color = RED2,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = "Vehicles per Hour",
                                x_line1_title = paste(input$month, "Throughput (vph)"),
                                plot_title = "Throughput (peak veh/hr) Trend")
})
```


### Arrivals on Green

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, warning = FALSE}
renderPlotly({
    get_bar_line_dashboard_plot(mr()$wk$aog, mr()$mo$aogd, mr()$mo$aogh,
                                "aog", "percent", highlight_color = RED2,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = paste(input$month, "AOG"),
                                x_line1_title = "AOG Trend",
                                x_line2_title = paste(input$month, "AOG by TOD"),
                                plot_title = "Percent Arrivals on Green")
})
```


### Queue Spillback Rate

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({
    get_bar_line_dashboard_plot(mr()$wk$qs, mr()$mo$qsd, mr()$mo$mqsh,
                                "qs_freq", "percent", highlight_color = RED2,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = paste(input$month, "Queue Spillback Rate"),
                                x_line1_title = "Queue Spillback Trend",
                                x_line2_title = paste(input$month, "Queue Spillback by TOD"),
                                plot_title = "Queue Spillback Rate")
})
```


### Split Failures

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, warning = FALSE}
renderPlotly({
    get_bar_line_dashboard_plot(mr()$wk$sf, mr()$mo$sfd, mr()$mo$sfh,
                                "sf_freq", "percent", highlight_color = RED2,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = paste(input$month, "Split Failures Rate"),
                                x_line1_title = "Split Failures Trend",
                                x_line2_title = paste(input$month, "Split Failures by TOD"),
                                plot_title = "Split Failures Rate")
})
```


### Travel Time Metrics

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({
    get_tt_plot(cor$mo$tti, cor$mo$ttih, 
                cor$mo$pti, cor$mo$ptih,
                month_ = current_month(),
                zone_group_ = zone_group(),
                x_bar_title = paste(input$month, "TTI & PTI"),
                x_line1_title = paste(input$month, "TTI by hr"),
                x_line2_title = paste(input$month, "PTI by hr"))
})
```









Volumes
=====================================

Row
-------------------------------------

### Traffic Volume [veh/day] {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
    value = get_valuebox(mr()$mo$vpd, "vpd", as_int,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart"
  )
})
```

### AM Peak Volume [veh/hr] {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$vphp$am, "vph", as_int,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-area-chart"
  )
})
```

### PM Peak Volume [veh/hr] {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$vphp$pm, "vph", as_int,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-area-chart"
  )
})
```

Row {.tabset .tabset-fade}
-------------------------------------

### Daily Volume

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({ # Good version
    get_bar_line_dashboard_plot(mr()$wk$vpd, mr()$mo$vpd, NULL,
                                "vpd", "integer", highlight_color = GDOT_BLUE,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = "Vehicles per Day",
                                x_line1_title = paste(input$month, "Daily Volume (vpd)"),
                                plot_title = "Daily Volume (veh/day) Trend")
})
```

### Monthly Change

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({
    get_pct_ch_plot(mr()$mo$vpd,
                    month_ = current_month(),
                    zone_group = zone_group())
})
```

### Peak Hour Volumes

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({
    am_vph_plot <- get_bar_line_dashboard_plot(mr()$wk$vphp$am,
                                               mr()$mo$vphp$am, NULL,
                                "vph", "integer", highlight_color = GDOT_BLUE,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = "Vehicles per Hour",
                                x_line1_title = paste(input$month, "Hourly Volume (vph)"),
                                plot_title = "Peak Period Hourly Volume (veh/hr) Trend")
    pm_vph_plot <- get_bar_line_dashboard_plot(mr()$wk$vphp$pm,
                                               mr()$mo$vphp$pm, NULL,
                                "vph", "integer", highlight_color = GDOT_BLUE,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = "Vehicles per Hour",
                                x_line1_title = paste(input$month, "Hourly Volume (vph)"),
                                plot_title = "Peak Period Hourly Volume (veh/hr) Trend")
    subplot(am_vph_plot, pm_vph_plot, nrows = 1, margin = 0.04)
})
```

### Hourly Volumes


```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}
renderPlotly({
    get_minmax_hourly_plot(mr()$mo$vph,
                           month_ = current_month(), 
                           zone_group_ = zone_group())
})
```









Equipment
=====================================

Row
-------------------------------------

### Vehicle Detector Availability {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$du %>% 
                          group_by(Corridor) %>% 
                          mutate(delta = uptime.all - lag(uptime.all)), 
                      "uptime.all", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-car"
  )
})
```

### CCTV Availability {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
    value = get_valuebox(cor$mo$cctv, "uptime", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "glyphicon-facetime-video" 
  )
})
```

### Pedestrian Detector Availability {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(cor$mo$ped, "uptime", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "fa-child" 
  )
})
```

### Communications Uptime {.value-box}

```{r, warning = FALSE}
renderValueBox({
  valueBox(
      value = get_valuebox(mr()$mo$cu, "uptime", as_pct,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
      icon = "ion-paper-airplane"
  )
})
```

Row {.tabset .tabset-fade}
-------------------------------------

### Detector Uptime

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}

renderPlotly({
    
    if (corridor() == "All Corridors") {

        get_cor_det_uptime_plot(mr()$dy$du, 
                                month_name = input$month,
                                month_ = current_month(), 
                                zone_group_ = zone_group())
        
    } else {
        
        get_uptime_plot(sig$dy$du, 
                                 sig$mo$du, 
                                 var_ = "uptime.all", 
                                 num_format = "percent", 
                                 month_ = current_month(), 
                                 zone_group_ = zone_group(),
                                 x_bar_title = "Current Month Uptime",
                                 x_line1_title = "Daily Uptime",
                                 plot_title = "",
                                 goal = NULL)
    }
})
```

### Pedestrian Detector Uptime

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, warning = FALSE}
renderPlotly({
    
    weekly_ped_df <- rename(cor$mo$ped, Date = Month) %>%
        filter(Date >= ymd("2017-07-01"))
    monthly_ped_df <- cor$mo$ped %>%
        filter(Month >= ymd("2017-07-01"))
    get_bar_line_dashboard_plot(weekly_ped_df,
                                monthly_ped_df,
                                var_ = "uptime", num_format = "percent", highlight_color = BROWN,
                                month_ = current_month(), zone_group_ = zone_group(),
                                x_bar_title = paste(input$month, "Ped Det Uptime"),
                                x_line1_title = "Pedestrian Detector Uptime Trend",
                                plot_title = "Ped Detector Uptime")
})
```

### CCTV Uptime

```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, warning = FALSE}

renderPlotly({
    
    if (corridor() == "All Corridors") {
        
        weekly_cctv_df <- cor$wk$cctv %>%
            filter(Date >= ymd("2017-07-01"))
        monthly_cctv_df <- cor$mo$cctv %>%
            filter(Month >= ymd("2017-07-01"))
        get_bar_line_dashboard_plot(weekly_cctv_df,
                                    monthly_cctv_df,
                                    var_ = "uptime",
                                    num_format = "percent",
                                    highlight_color = BROWN,
                                    month_ = current_month(), 
                                    zone_group_ = zone_group(),
                                    x_bar_title = paste(input$month, "CCTV Uptime"),
                                    x_line1_title = "CCTV Uptime Trend",
                                    plot_title = "CCTV Uptime")
    } else {
        
        plot_individual_cctvs(sig$dy$cctv, 
                              month_ = current_month(), 
                              zone_group_ = zone_group(),
                              corridor_ = corridor())
    }
    
})
```




### Communications Uptime


```{r, fig.width = FIG_WIDTH, fig.height = FIG_HEIGHT, eval = TRUE, warning = FALSE}

renderPlotly({

    if (corridor() == "All Corridors") {
        
        get_cor_comm_uptime_plot(mr()$dy$cu,
                                 mr()$mo$cu,
                                 month_name = input$month,
                                 month_ = current_month(),
                                 zone_group_ = zone_group())
    } else {
        
        get_uptime_plot(sig$dy$cu, 
                                 sig$mo$cu, 
                                 var_ = "uptime", 
                                 num_format = "percent", 
                                 month_ = current_month(), 
                                 zone_group_ = zone_group(),
                                 x_bar_title = "Current Month Uptime",
                                 x_line1_title = "Daily Uptime",
                                 plot_title = "",
                                 goal = NULL)
    }
    
})
```









Activity
=====================================

Row
-------------------------------------

### TEAMS Tasks Reported This Month {.value-box}

```{r, eval = TRUE, warning = TRUE}
renderValueBox({
  valueBox(
    value = get_valuebox(rename(cor$mo$events, delta = delta.rep), "Reported", as_int,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart"
  )
})
```

### TEAMS Tasks Resolved This Month {.value-box}

```{r, eval = TRUE, warning = TRUE}
renderValueBox({
  valueBox(
    value = get_valuebox(rename(cor$mo$events, delta = delta.res), "Resolved", as_int,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart"
  )
})
```

### TEAMS Tasks Outstanding (Unresolved) {.value-box}

```{r, eval = TRUE, warning = TRUE}
renderValueBox({
  valueBox(
    value = get_valuebox(rename(cor$mo$events, delta = delta.out), "Outstanding", as_int,
                           zone = zone_group(), mo = current_month(), break_ = FALSE),
    icon = "fa-area-chart"
  )
})
```


Row {.tabset .tabset-fade data-height=800}
------------------------------------------

### TEAMS

```{r eval = TRUE, warning = FALSE}

fillRow(
    fillCol(
        renderPlotly({ 
            data.set <- gather_outstanding_events(
                filter(cor$mo$events, Zone_Group == zone_group() & 
                           Month <= current_month())
            )
            validate(need(nrow(data.set) > 0, "No Data"))
            cum_events_plot(data.set)
        }),
        renderPlotly({ 
            data.set <- filter(teams_tables$type, Zone_Group == zone_group() & 
                                   Month == current_month())
            validate(need(nrow(data.set) > 0, "No Data"))
            plot_teams_tasks(data.set,
                             var_ = "Task_Type",
                             title_ = "Incidents This Month by Type (top), Source (bottom)", 
                             height_ = 250) 
        }), 
        renderPlotly({ 
            data.set <- filter(teams_tables$source, Zone_Group == zone_group() & 
                                   Month == current_month())
            validate(need(nrow(data.set) > 0, "No Data"))
            plot_teams_tasks(data.set,
                             var_ = "Task_Source", 
                             height_ = 150) 
        }), 
        height = 800, flex = c(NA, NA, 1)), 
        
    fillCol(
        renderPlotly({ 
            data.set <- filter(teams_tables$subtype, Zone_Group == zone_group() & 
                                   Month == current_month())
            validate(need(nrow(data.set) > 0, "No Data"))
            plot_teams_tasks(data.set,
                             var_ = "Task_Subtype",
                             title = "Incidents This Month by Subtype", 
                             textpos = "outside", 
                             height_ = 700) 
        }),
        height = 800))
```





### RTOP Activity Logs


#### **Download TSOS Monthly Reports (docx)**

[January 2018](https://s3.amazonaws.com/gdot-devices/TSOS+Monthly+Meeting+Report+-+2018-01.docx) | 
[February 2018](https://s3.amazonaws.com/gdot-devices/TSOS+Monthly+Meeting+Report+-+2018-02.docx) | 
[March 2018](https://s3.amazonaws.com/gdot-devices/TSOS+Monthly+Meeting+Report+-+2018-03.docx) | 
[April 2018](https://s3.amazonaws.com/gdot-devices/TSOS+Monthly+Meeting+Report+-+2018-04.docx) | 
May 2018 | 
[June 2018](https://s3.amazonaws.com/gdot-devices/TSOS+Monthly+Meeting+Report+-+2018-06.docx) | 
[July 2018](https://s3.amazonaws.com/gdot-devices/TSOS+Monthly+Meeting+Report+-+2018-07.docx) | 
August 2018


#### **Download Traffic Engineers' Activity Reports (pdf)**


**RTOP 1**

Zone 1: 
[SR 13/42/155](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+13-42-155.pdf) | 
[SR 141S](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+141S.pdf) | 
[SR 237](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+237.pdf) | 
[SR 9-Atlanta](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+9-Atlanta.pdf)

Zone 2: 
[SR 120W](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+120W.pdf) | 
[SR 140-Roswell](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+140-Roswell.pdf) | 
[SR 280](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+280.pdf) | 
[SR 360](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+360.pdf) | 
[SR 3N](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+3N.pdf) | 
[SR 92](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+92.pdf) | 
[SR 9N](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+9N.pdf)

Zone 3: 
[SR 138](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+138.pdf) | 
[SR 3S](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+3S.pdf) | 
[SR 85](https://s3.amazonaws.com/gdot-devices/RTOP1/latest/SR+85.pdf)


**RTOP 2**

Zone 4: 
[US 278](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+8W+US+278.pdf) | 
[SR 3](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+3.pdf) | 
[SR 5](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+5.pdf) | 
[SR 6](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+6.pdf)

Zone 5: 
[SR 10](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+10.pdf) | 
[SR 12](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+12.pdf) | 
[SR 154](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+154.pdf) | 
[SR 155S](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+155S.pdf) | 
[SR 42](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+42.pdf) | 
[SR 8W-DeKalb](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+8W+Dekalb.pdf) | 
[SR 8W-Ponce](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+8W+Ponce.pdf)

Zone 6: 
[SR 120E](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+120.pdf) | 
[SR 140-Gwinnett](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+140.pdf) | 
[SR 141N](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+141.pdf) | 
[SR 20](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+20.pdf) | 
[SR 8E](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+8E.pdf) | 
[SR 9-Alpharetta](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/SR+9.pdf)

Zone 7: 
[Zone 7](https://s3.amazonaws.com/gdot-devices/RTOP2/latest/Zone+7.pdf)









Signals List
=====================================

Row {data-height = 800}
-------------------------------------

```{r}
renderDataTable({
    
    datatable(filtered_corridors(),  #corr, 
              escape = FALSE,
              extensions = 'Scroller', 
              options = list(
                  deferRender = TRUE,
                  scrollY = 800,
                  scroller = TRUE,
                  searching = TRUE)
    )
})
```









Signal Details
=====================================

```{r signal_detail}
fillCol(height = 100,
renderUI({
    selectInput("signalid", "SignalID:",
                choices = c("Select", filtered_signalids()),
                selected = "",
                width = "600px")
}))


fillCol(height = 700,

    renderPlotly({
        if (input$signalid == "Select") {
            no_data_plot("")
        } else {
            tryCatch({
                sid <- stringr::str_extract(input$signalid, "^(\\d+)(?=:)")
                #signal_dashboard_cached_plot(sid)
                signal_dashboard(sid)
            }, error = function(e) {
                no_data_plot("")
            })
        }
    })
)
```










Explanation of Calcs
=====================================

### PERFORMANCE

#### **Throughput**

Throughput is a measure of efficiency. It is meant to represent the maximum
number of vehicles serviced through an intersection, and the corridor.

Throughput is calculated as the highest 15-minute volume in a day for
each intersection, converted to an hourly volume, averaged over the
corridor. Volumes come from high-resolution event logs from the controller,
which are stored in the ATSPM database.

#### **Arrivals on Green**

Arrivals on Green (AOG) is a measure of coordination. A percentage of 
vehicles arriving on green would be due to good offsets
and should be correlated with fewer stops and less delay.

AOG is calculated as the total number of vehicles arriving on green
divided by the total number of arrivals. It includes main street through phases,
during peak periods (6am-10am, 3pm-7pm) on Tuesdays, Wednesdays and
Thursdays.

The calculation takes the ATSPM data, aggregates the counts by cycle and
interval, and divides the counts in the green intervals by the total counts
for the cycle, averaged over all cycles.

#### **Queue Spillback Rate**

Queue Spillback Rate is an experimental measure of effectiveness.
It is a measure of unmet demand in a cycle. Based on the vehicle
dwell times over setback detectors on the main street through phases, each cycle is
evaluated for spillback. A spillback condition will be triggered by
occupancy readings above what is typical for setback detectors under
freely flowing conditions. 

Specifically, under freely flowing
conditions, the time between subsequent detector on and off events is typically
around 0.1 seconds for setback detectors. 
When the 95^th^ percentile detector occupancy duration increases above 3
seconds in a cycle, it will be assumed there is standing traffic on the setback
detector and a spillback event will be flagged for that phase in that
cycle.

The queue spillback rate is calculated as the number of spillback events
divided by the number of cycles for main street through phases.

#### **Split Failures**

Split failure is another measure of unmet demand. It identifies cycles where a
phase has unserved demand. A phase is flagged for split failure when a  detector on event occurs
before the start of red and the subsequent detector off event occurs after the next
start of green.

Because this measure requires stop
bar detection, it is only be calculated for side street and left
turn phases, i.e., all phases other than main street through phases.

Split Failure Percent is calculated as the number of split failures divided by the total
number of side street and left turn phases.

#### **Travel Time Index**

Travel Time Index (TTI) is a measure of delay on the corridor. It is the
ratio of travel time to free flow travel time.

Hourly travel time data from HERE queried from RITIS. Free flow travel
times are based on the "reference speed" value from HERE for each
segment. Travel time and free flow travel time are calculated for each
corridor by summing over all segments in the corridor for every hour in
the month.

An hourly Travel Time Index is then calculated for each corridor as the
average travel time for that hour of the day divided by the free flow
travel time for the corridor. The TTI for each hour is then averaged
over the day, weighted by the average hourly volume on the main street through phases
(from ATSPM) to get a TTI for the month (this gives more weight to peak
periods than off-peak periods).

#### **Planning Time Index**

The Planning Time Index (PTI) calculation uses the same data as the
Travel Time Index. However, instead of taking the average travel times
for each hour of the day, it takes the 90^th^ percentile for each hour,
over the days of the month. These 90^th^ percentile travel times are
then averaged over the day, weighted by the average hourly volume from
the main street through phases  (from ATSPM) to get a PTI for the month 
(this gives more weight to peak periods than off-peak periods).



### VOLUMES

#### **Daily Volume**

Volume is a measure of demand on a corridor. Total volume on main street 
through phases are summed over each Tuesday, Wednesday and Thursday,
and then averaged over all days in the month.

#### **Monthly Change**

Each bar in the Monthly Change plot shows the percent change in daily volume
compared with the previous month.

#### **Peak Hour Volumes**

The AM and PM average peak hour volumes are the average hourly volume
for the month over the AM and PM peak hours, respectively. 
Peak hours are 6am-10am, 3pm-7pm.

#### **Hourly Volumes**

The hourly volumes chart shows the range of hourly volumes for all
months from the beginning of the data set, superimposed with the hourly
volumes for the current month. It is meant to show the spread of each
hour and whether the current month is high or low compared to the
historical range.

### EQUIPMENT AND ACTIVITY

#### **Detector Uptime**

Detector Uptime is a measure of state-of-good-repair, which may be correlated to
other performance measures since failed detectors may negatively affect
performance.

Based on hourly volumes by detector, each hour is flagged if any of the
following conditions apply:

-   Missing data (volume = NA)

-   volume &gt; 1000

-   Absolute change in volume from previous hour &gt; 500

-   change in volume from previous hour = 0

For each day, if more than 40% of hours are flagged the detector is considered down for that day.
Separately, if the average absolute change from the previous hour, averaged over the day, is
greater than 200, the detector is considered down fot that day. The
uptime is the percentage of good days in the month. These thresholds are
all based on observation of the data and can be adjusted as necessary.

#### **Pedestrian Detector Uptime**

Pedestrian Detector Uptime is the percentage of pedestrian pushbuttons operational and is
reported by Corridor Managers from physically pressing each button in
the field at some point during the month and observing whether it is
working.

There are two reasons why this is currently done manually. The first is that
multiple push buttons are often physically wired into the same detector input,
making it impossible from the controller inputs to determine whether both push
buttons are working, or just one. The second is due to the relatively infrequent calls,
it is difficult to tell from the data whether there is no demand or whether the 
push button has failed.

#### **CCTV Uptime**

Through December 2017, CCTV Uptime was reported by Corridor Managers in their 
monthly reports. In January, 2018, it came from TSOS based on a manual check
of each camera during the month and reporting whether it returns an
image and whether it can be controlled (pan-tilt-zoom).

As of February 2018, CCTV Uptime is calculated based on the image returned from
the Georgia 511 website. If there is a live image, it will considered
working as of its "last modified" timestamp from the website.

#### **Communications Uptime**

This is calculated from gaps in the ATSPM high resolution data. Any gaps
in subsequent events greater than 15 minutes are considered to be due to 
communication loss. The sum of these gaps converted to a percent is the
daily communication uptime for that controller. If comms are lost for all
intersections, it is considered a system failure and that time is excluded
from the uptime calculation.

#### **Events Reported, Resolved, Outstanding**

Activity measures come from TEAMS reports from data as entered by corridor managers.
TEAMS is GDOT's ticketing and tracking system for signal equipment and 
incident-related activity.

All events reported in the month are counted, as are the number of
events resolved in the month. The number of outstanding events is the
cumulative sum of reported events less the cumulative sum of resolved
events.

#### **RTOP Activity Logs**

These are the monthly reports produced monthly by RTOP Corridor Managers detailing key activities, maintenance tasks and action items for the month.

