---
title: "MARK 1 Watchdog (beta)"
resource_files:
- AthenaJDBC42_2.0.9.jar
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    css: style.css
    favicon: GDOTLogo.svg
    logo: GDOTLogo.svg
    orientation: rows
    self_contained: no
    vertical_layout: scroll
---

<style>

.table thead tr th:nth-child(2n+4) {
    /*color: white;*/
    visibility: hidden;
    font-size:1px;
    width:"50px";
}

.table thead tr th:nth-child(2) {
    width:"1000px";
}

</style>


```{r global, cache = FALSE, include = FALSE, warning = FALSE}
# FLEXDASHBOARD - RTOP_MONTHLY_REPORT

conf_mode <- "beta"

source("Monthly_Report_UI_Functions.R")


FIG_WIDTH = 14
FIG_HEIGHT = 7



```









Inputs {.sidebar}
=====================================

Measurement, Accuracy, and Reliability Kit (MARK 1) 

Past month reports can be viewed back to `r format(first_month, "%B %Y")`.


RTOP Concept of Operations can be found 
`r tags$a(href = "https://s3.amazonaws.com/gdot-spm/GDOT_STORM-COO.pdf", 
           target = "_blank",
           "here")`


```{r sidebar, warning = FALSE, cache = FALSE}
# shiny inputs defined here



selectInput("month", "Month:",
                       choices = month_options,
                       selected = month_options[1]) # Default to current month

selectInput("zone_group", "Signal Group:",
                       choices = zone_group_options,
                       selected = "All RTOP")



# Corridor Selection Drop Down based on Zone/Zone Group ---

conditionalPanel("input.zone_group != 'All RTOP'",
                 selectInput("corridor_x", "Corridor:",
                             choices = c("All Corridors"),
                             selected = "All Corridors"))

observe({
    choices_ <- if (is.null(input$zone_group)) {
                    NULL
                } else {
                    if (input$zone_group == "All RTOP") {
                        c("All Corridors")
                    } else if (input$zone_group %in% c("RTOP1", "RTOP2")) {
                        c("All Corridors",
                          as.character(unique(filter(
                              corridors, Zone_Group == input$zone_group)$Corridor)))
                    } else {
                        c("All Corridors",
                          as.character(unique(filter(
                              corridors, Zone == input$zone_group)$Corridor)))
                    }
                }
            
    updateSelectInput(session, "corridor_x", choices = sort(choices_), selected = "All Corridors")
})


# --- Sub-Corridor Selection Drop Down based on Corridor ---

conditionalPanel(
    "input.corridor_x != 'All Corridors'",
    radioButtons(
        "subcorridors", 
        label = NULL, 
        choices = c("By Intersection", "By Sub-corridor"), 
        selected = "By Intersection",
        inline = FALSE, 
        width = NULL, 
        choiceNames = NULL,
        choiceValues = NULL)
)


# --- -------------------------------------------------- ---


current_month <- reactive(lubridate::dmy(paste(1, input$month)))
endof_current_month <- reactive(lubridate::dmy(paste(1, input$month)) + months(1) - days(1))
current_quarter <- reactive(as.character(lubridate::quarter(current_month(), with_year = TRUE)))


# This is a simpler version of what is commented out below
corridor <- reactive({
    if (input$zone_group == "All RTOP") {
        "All Corridors"
    } else {
        input$corridor_x
    }
})



zone_group <- reactive(
    if (corridor() == "All Corridors") {
        input$zone_group
    } else {
        corridor()
    }
)


mr <- reactive(
    if (corridor() == "All Corridors") {
        cor
    } else if (input$subcorridors == "By Sub-corridor") {
        sub
    } else {
        sig
    }
)

filtered_corridors <- reactive({

    # All RTOP is the union of RTOP1, RTOP2
    if (input$zone_group == "All RTOP") {
        corr <- corridors %>% 
            filter(Zone_Group %in% c("RTOP1", "RTOP2"))

    # Zone 7 is the union of Zone 7m, 7d
    } else if (input$zone_group == "Zone 7") {
        corr <- corridors %>% 
            filter(grepl("^Zone 7", Zone))

    # Zones filter by Zone rather than Zone_Group
    } else if (startsWith(input$zone_group, "Zone")) {
        corr <- corridors %>% 
            filter(Zone %in% input$zone_group)

    } else {
        corr <- corridors %>% 
            filter(Zone_Group %in% input$zone_group)
    }
    
    # if a specific corridor is selected, filter on that
    if (corridor() != "All Corridors") {
        corr <- corr %>% 
            filter(Corridor == corridor())
    } 
    
  
    corr %>% select(-Description, -Asof)
})




filtered_signalids <- reactive(paste0(filtered_corridors()$SignalID, ": ",
                                      filtered_corridors()$Name))


mr_str <- reactive(
    if (corridor() == "All Corridors") {
        "cor"
    } else if (input$subcorridors == "By Sub-corridor") {
        "sub"
    } else {
        "sig"
    }
)

# renderText({"\nSelected Month"})
# renderPrint({current_month()})
# 
# renderText({"\nEnd of Selected Month"})
# renderPrint({endof_current_month()})
# 
# renderText({"Selected Querter"})
# renderPrint({current_quarter()})
# 


# renderText({"Selected Zone Group"})
# renderPrint({zone_group()})
# 
# renderText({"Selected Corridor"})
# renderPrint({corridor()})
# 
# renderText({"Sub-Corridors selected"})
# renderPrint({input$subcorridors})
# 
# renderText({"Filtered Corridors"})
# renderPrint({filtered_corridors()})
# 
# renderText({"mr()"})
# renderPrint({mr_str()})

# renderText({"env"})
# renderPrint({Sys.getenv("AWS_ACCESS_KEY_ID")})
# 
# renderText({"conf"})
# renderPrint({aws_conf$AWS_ACCESS_KEY_ID})




filtered_signalids <- reactive(paste0(filtered_corridors()$SignalID, ": ",
                                      filtered_corridors()$Name))

#renderText({"Mode:"})
#renderPrint({conf_mode})
#renderPrint({conf$mode})


# renderText({"\nSelected Month"})
# renderPrint({current_month()})
# 
# renderText({"Selected Zone Group"})
# renderPrint({zone_group()})
# 
# renderText({"Selected Corridor"})
# renderPrint({corridor()})
```









Watchdog
=====================================

Row {data-height = 92}
-------------------------------------

```{r watchdog, fig.height = 0.92}

plot_height <- reactive({

    n <- filtered_alerts()$intersections
    css_px <- as.character(50 + n * 14)
    paste0(css_px, "px")
})

filtered_alerts <- reactive({

    alerts_by_date <- filter_alerts_by_date(alerts, input$date_range)
    
    phase_ <- if(input$phase.eight != "All") {
        input$phase.eight
    } else {
        "All"
    }

    filter_alerts(alerts_by_date,
                  input$alert_type,
                  zone_group(),
                  corridor(),
                  phase_,
                  input$id_filter)
})
    


output$alerts_plot <- renderPlot({

    dataset <- filtered_alerts()

    if (nrow(dataset$plot) > 0) {
        
        plot_df <- dataset$plot %>% 
            mutate(signal_phase = if_else(
                Zone_Group == "Ramp Meters",
                stringr::str_replace(signal_phase, " \\| ", glue(" | {ApproachDesc} | ")),
                as.character(signal_phase))) %>%
            mutate(signal_phase = factor(signal_phase))
        
        if (nrow(plot_df) > 0) {
            plot_alerts(plot_df, input$date_range)
        } else {
            plot_empty(zone_group)
        }

    } else {
        plot_empty(zone_group)
    }
})


# Main panel with tabs: Map, Table, Plots
fluidRow(
    column(
        width = 3,
        dateRangeInput(
            "date_range", "Date Range:",
            start = today() - days(14),
            end = today(),
            min = today() - days(365),
            max = today(),
            format = "mm/dd/yy", 
            startview = "month", 
            weekstart = 0,
            separator = " - ")
    ),
    column(
        width = 3,
        selectInput(
            "alert_type", "Alert:",
            choices = c("No Camera Image",
                        "Bad Vehicle Detection",
                        "Bad Ped Detection",
                        "Pedestrian Activations",
                        "Force Offs",
                        "Max Outs",
                        "Count",
                        "Missing Records"),
            selected = "No Camera Image")
    ),
    column(
        width = 2,
        conditionalPanel(
            "(input.alert_type == 'Missing Records') ||
             (input.alert_type == 'No Camera Image')",
            selectInput("phase.all", "Phase:",
                        choices = "All",
                        selected = "All")),
        conditionalPanel(
            "(input.alert_type == 'Pedestrian Activations') || 
            (input.alert_type == 'Force Offs') ||
            (input.alert_type == 'Max Outs') ||
            (input.alert_type == 'Count') ||
            (input.alert_type == 'Bad Vehicle Detection') ||
            (input.alert_type == 'Bad Ped Detection')",
            selectInput("phase.eight", "Phase:",
                        choices = c("All", seq_len(8)),
                        selected = "All"))
    ),
    column(
        width = 4,
        textInput("id_filter", "Intersection Filter:")
    )
)
```

Row {data-height = 800}
-------------------------------------

```{r}
fillRow(
    tabsetPanel(
        type = "tabs",
        tabPanel(
            "Plot", 
            helpText(
                paste("Use the 'Intersection Filter' to reduce the size of the list.",
                      "Filter on the intersection name or ID.")),
                renderUI({
                    
                    shiny::validate(
                        need(filtered_alerts()$intersections < 2000, 
                             paste("\n\n\nTOO MUCH DATA TO PLOT.",
                                   "Select a Zone, Corridor of Phase", 
                                   "to reduce the number of records.")))
                    
                    plotOutput("alerts_plot",
                               height = plot_height())
                })
        ),
        tabPanel(
            "Table", 
            renderDataTable({
                datatable(filtered_alerts()$table, 
                          escape = FALSE,
                          extensions = 'Scroller', 
                          options = list(
                              deferRender = TRUE,
                              scrollY = 500,
                              scroller = TRUE,
                              searching = FALSE))
            }),
            downloadHandler('watchdog_alerts.csv', content = function(file) {
                write_csv(filtered_alerts()$table, file)
            })
        )
    )
)
```







Signals List
=====================================

Row {data-height = 800}
-------------------------------------

```{r}
renderDataTable({
    
    datatable(filter(filtered_corridors(), as.integer(as.character(SignalID)) > 0),
              escape = FALSE,
              extensions = 'Scroller', 
              options = list(
                  deferRender = TRUE,
                  scrollY = 800,
                  scroller = TRUE,
                  searching = TRUE)
    )
})
```








Signal Details
=====================================

```{r signal_detail, eval = TRUE}
fillCol(height = 100,
    
    fluidRow(
        column(width = 4,
        renderUI(selectInput("signalid", "Select Signal:",
                    choices = c("Select", filtered_signalids()[!startsWith(filtered_signalids(), "-1")]),
                    selected = "",
                    width = "800px"))),
        column(width = 1,
        tags$div(class = "plot-signal-details-button",
                 actionButton("signal_details_button", "Plot")))
    )
)

sid <- eventReactive(input$signal_details_button, {
    req(input$signalid)
    sub(":.+", "", input$signalid)
})


fillCol(height = 700,

        renderPlotly({
          
            #signal_dashboard_athena(sid(), current_month(), conf$athena)
            detector_dashboard_athena(sid(), current_month(), conf$athena)
        })
)
```
