---
# ------------------------------
title: "MARK 1"                      # Production
# ------------------------------
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    logo: GDOTLogo.svg
    favicon: GDOTLogo.svg
    css: style.css
    includes:
        in_header: google-analytics.html
runtime: shiny
---

<style>

.table thead tr th:nth-child(2n+4) {
    /*color: white;*/
    visibility: hidden;
    font-size:1px;
    width:"50px";
}

.table thead tr th:nth-child(2) {
    width:"1000px";
}

</style>


```{r globals, context="data", cache=FALSE, include = FALSE, warning = FALSE}
# FLEXDASHBOARD - RTOP_MONTHLY_REPORT

conf_mode <- "production"

library(flexdashboard)
source("Monthly_Report_UI_Functions.R")

FIG_WIDTH = 14
FIG_HEIGHT = 7

corridors <- read_feather("all_corridors.feather")
cor <- readRDS("cor.rds")
sig <- readRDS("sig.rds")
sub <- readRDS("sub.rds")

# cor <- s3readRDS(bucket = "gdot-spm", object = "mark/cor.rds")
# sig <- s3readRDS(bucket = "gdot-spm", object = "mark/sig.rds")
# sub <- s3readRDS(bucket = "gdot-spm", object = "mark/sub.rds")
alerts <- aws.s3::s3readRDS("mark/watchdog/alerts.rds", "gdot-spm")
```







Inputs {.sidebar}
=====================================

Measurement, Accuracy, and Reliability Kit (MARK 1)

Past month reports can be viewed back to `r format(first_month, "%B %Y")`.


RTOP Concept of Operations can be found
`r tags$a(href = "https://s3.amazonaws.com/gdot-spm/GDOT_STORM-COO.pdf",
           target = "_blank",
           "here")`


```{r sidebar, context="render", warning = FALSE, cache = FALSE}
# shiny inputs defined here



selectInput("month", "Month:",
                       choices = month_options,
                       selected = month_options[1]) # Default to current month

selectInput("zone_group", "Signal Group:",
                       choices = zone_group_options,
                       selected = "All RTOP")



# Corridor Selection Drop Down based on Zone/Zone Group ---

conditionalPanel("input.zone_group != 'All RTOP'",
                 selectInput("corridor_x", "Corridor:",
                             choices = c("All Corridors"),
                             selected = "All Corridors"))

observe({
    choices_ <- if (is.null(input$zone_group)) {
                    NULL
                } else {
                    if (input$zone_group == "All RTOP") {
                        c("All Corridors")
                    } else if (input$zone_group %in% c("RTOP1", "RTOP2")) {
                        c("All Corridors",
                          as.character(unique(filter(
                              corridors, Zone_Group == input$zone_group)$Corridor)))
                    } else {
                        c("All Corridors",
                          as.character(unique(filter(
                              corridors, Zone == input$zone_group)$Corridor)))
                    }
                }

    updateSelectInput(session, "corridor_x", choices = choices_, selected = "All Corridors")
})

# --- Sub-Corridor Selection Drop Down based on Corridor ---

conditionalPanel(
    "input.corridor_x != 'All Corridors'",
    radioButtons(
        "subcorridors",
        label = NULL,
        choices = c("By Intersection", "By Sub-corridor"),
        selected = "By Intersection",
        inline = FALSE,
        width = NULL,
        choiceNames = NULL,
        choiceValues = NULL)
)

# div("\nSelected Month")
# textOutput("selected_current_month")
# 
# div("\nEnd of Selected Month:")
# textOutput("selected_endof_current_month")
# 
# 
# div("\nSelected Quarter:")
# textOutput("selected_current_quarter")
# 
# div("\nSelected Zone Group:")
# textOutput("selected_zone_group")
# 
# div("\nSelected Corridor:")
# textOutput("selected_corridor")
# 
# div("\nSub-Corridors Selected:")
# textOutput("selected_subcorridors")
# 
# div("\nFiltered Corridors:")
# textOutput("selected_filtered_corridors")
# 
# div("\nmr():")
# textOutput("selected_mr_str")
```


```{r, context="server"}

current_month <- reactive(lubridate::dmy(paste(1, input$month)))
endof_current_month <- reactive(lubridate::dmy(paste(1, input$month)) + months(1) - days(1))
current_quarter <- reactive(as.character(lubridate::quarter(current_month(), with_year = TRUE)))


# This is a simpler version of what is commented out below
corridor <- reactive({
    if (input$zone_group == "All RTOP") {
        "All Corridors"
    } else {
        input$corridor_x
    }
})


zone_group <- reactive(
    if (corridor() == "All Corridors") {
        input$zone_group
    } else {
        corridor()
    }
)


mr <- reactive(
    if (corridor() == "All Corridors") {
        cor
    } else if (input$subcorridors == "By Sub-corridor") {
        sub
    } else {
        sig
    }
)

filtered_corridors <- reactive({

    # All RTOP is the union of RTOP1, RTOP2
    if (input$zone_group == "All RTOP") {
        corr <- corridors %>%
            filter(Zone_Group %in% c("RTOP1", "RTOP2"))

    # Zone 7 is the union of Zone 7m, 7d
    } else if (input$zone_group == "Zone 7") {
        corr <- corridors %>%
            filter(grepl("^Zone 7", Zone))

    # Zones filter by Zone rather than Zone_Group
    } else if (startsWith(input$zone_group, "Zone")) {
        corr <- corridors %>%
            filter(Zone %in% input$zone_group)

    } else {
        corr <- corridors %>%
            filter(Zone_Group %in% input$zone_group)
    }

    # if a specific corridor is selected, filter on that
    if (corridor() != "All Corridors") {
        corr <- corr %>%
            filter(Corridor == corridor())
    }

    corr %>% select(-Description, -Asof)
})




filtered_signalids <- reactive({
    x <- filtered_corridors() %>% filter(as.integer(as.character(SignalID)) > 0)
    paste0(x$SignalID, ": ", x$Name)
})


mr_str <- reactive(
    if (corridor() == "All Corridors") {
        "cor"
    } else if (input$subcorridors == "By Sub-corridor") {
        "sub"
    } else {
        "sig"
    }
)

output$selected_current_month <- renderText({current_month()})
output$selected_endof_current_month <- renderText({endof_current_month()})
output$selected_current_quarter <- renderText({current_quarter()})
output$selected_zone_group <- renderText({zone_group()})
output$selected_corridor <- renderText({corridor()})
output$selected_subcorridors <- renderText({input$subcorridors})
output$selected_filtered_corridors <- renderPrint({filtered_corridors()})
output$selected_mr_str <- renderText({mr_str()})

```










One-Month Summary
=====================================

Row {data-height = 50}
-------------------------------------

### Performance <a id = "page_performance"></a>

Arterial performance measures (% change from previous month)

Row
-------------------------------------

### Throughput [vph] {.value-box}

```{r, context="render"}
valueBoxOutput("tp_vb")
```

### Arrivals on Green {.value-box}

```{r, context="render"}
valueBoxOutput("aog_vb")
```

### Progression Ratio {.value-box}

```{r, context="render"}
valueBoxOutput("pr_vb")
```

### Spillback Rate {.value-box}

```{r, context="render"}
valueBoxOutput("qs_vb")
```

### Peak Period Split Failures {.value-box}

```{r, context="render"}
valueBoxOutput("sf_vb")
```

### Off-Peak Split Failures {.value-box}

```{r, context="render"}
valueBoxOutput("sfo_vb")
```

### Travel Time Index {.value-box}

```{r, context="render"}
valueBoxOutput("tti_vb")
```

### Planning Time Index {.value-box}

```{r, context="render"}
valueBoxOutput("pti_vb")
```


```{r, context="server"}
output$tp_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            mr()$mo$tp, 
            "vph", 
            as_int, 
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-bar-chart",
        color = BLUE
    )
})

output$aog_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            mr()$mo$aogd, 
            "aog", 
            as_pct,
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-car",
        color = BLUE
    )
})

output$pr_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            mr()$mo$prd, 
            "pr", 
            as_2dec,
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-car",
        color = BLUE
    )
})

output$qs_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            mr()$mo$qsd, 
            "qs_freq", 
            as_pct,
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-car",
        color = BLUE
    )
})

output$sf_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            mr()$mo$sfd, 
            "sf_freq", 
            as_pct,
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-car",
        color = BLUE
    )
})

output$sfo_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            mr()$mo$sfo,
            "sf_freq",
            as_pct,
            zone = zone_group(),
            mo = current_month(),
            break_ = TRUE
        ),
        icon = "fa-car",
        color = BLUE
    )
})

output$tti_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            cor$mo$tti, 
            "tti", 
            as_2dec,
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-dashboard",
        color = BLUE
    )
})

output$pti_vb <- renderValueBox({
    valueBox(
        value = get_valuebox(
            cor$mo$pti, 
            "pti", 
            as_2dec,
            zone = zone_group(), 
            mo = current_month(), 
            break_ = TRUE
        ),
        icon = "fa-dashboard",
        color = BLUE
    )
})
```

Row {data-height = 50}
-------------------------------------

### Volume-Based Measures

Corridor volumes (% change from previous month)

Row
-------------------------------------
